Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-05-17 ms.qmd
Supress messages

```{r}
#| label: fig-preds
#| fig-cap: Model predictions for the expected change in acclimation $lnCVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms. Predictions consider the uncertainty in random effects (i.e., species, phylogeny, study).

>>>>

```{r}
#| label: fig-preds
#| echo: false
#| warning: false
#| message: false
#| fig-cap: Model predictions for the expected change in acclimation $lnCVR_{Q_{10}}$ across the globe for terrestrial, marine and freshwater ecthotherms. Predictions consider the uncertainty in random effects (i.e., species, phylogeny, study).
